### 2023-02-21 manuscript.Rmd
Update manuscript.Rmd
merged github stars into later test as suggested by @aaronpeikert

@gartner2022responsible suggest the number of citations to evaluate the impact of a software package.
However, citations suffer from serious shortcomings when used to evaluate the impact of research software, particularly, when used comparatively in the context of hire and promotion.
For example, it is much more commonly accepted to cite data analysis packages than supporting packages (such as papaja [@R-papaja] used to render this article). 
Further, functionality of successful, modular scientific software is ideally reused in other software packages to avoid duplication of code and enable faster development of new software.
While we highly encourage this from both a software engineering perspective and for scientific progress, it challenges the validity of citation-based metrics for impact.
For example, consider the NLopt optimization suite, which counts 1,711 citations on Google scholar at the time of writing.
NLopt is a backbone for many scientific model fitting packages both because it implements various optimization algorithm but also because it is open-source and can inspire re-implementations of these algorithms.
For example, consider the famous lme4 package [@bates2014fitting] for generalized linear mixed-effects models, that is partly based on NLopt.
This package has more than 58,000 citations on Google scholar, yet it is unlikely that researchers will cite the underlying optimization algorithm.
<!--For example, the pdc package [@pdc-paper] offers functions to cluster time-series based on relative complexity.
As another example, the TSclust package [@TSclust] is a wrapper to several dissimilarity measures for clustering time series. 
Some of us maintain the pdc clustering package [@pdc-paper], which is contained in TSclust and we saw that researchers use the pdc approach but only cite the TSclust package.
-->
## ID 11: GitHub Stars

We object to the use of Github stars as a general metric.
First of all, it is tied only to a single, commercial platform.
More importantly, we question the validity of such metrics that, like rating systems on commercial platforms, are too easy to be gamed.

@@

In our opinion, total citation metrics, number of users, downloads per month and similar may provide a coarse measure for the impact of a software package, even though it is important to note the shortcomings we described above.

>>>>

@gartner2022responsible suggest the number of citations to evaluate the impact of a software package.
However, citations suffer from serious shortcomings when used to evaluate the impact of research software, particularly, when used comparatively in the context of hire and promotion.
For example, it is much more commonly accepted to cite data analysis packages than supporting packages (such as papaja [@R-papaja] used to render this article). 
Further, functionality of successful, modular scientific software is ideally reused in other software packages to avoid duplication of code and enable faster development of new software.
While we highly encourage this from both a software engineering perspective and for scientific progress, it challenges the validity of citation-based metrics for impact.
For example, consider the NLopt optimization suite, which counts 1,711 citations on Google scholar at the time of writing.
NLopt is a backbone for many scientific model fitting packages both because it implements various optimization algorithm but also because it is open-source and can inspire re-implementations of these algorithms.
For example, consider the famous lme4 package [@bates2014fitting] for generalized linear mixed-effects models, that is partly based on NLopt.
This package has more than 58,000 citations on Google scholar, yet it is unlikely that researchers will cite the underlying optimization algorithm.
<!--For example, the pdc package [@pdc-paper] offers functions to cluster time-series based on relative complexity.
As another example, the TSclust package [@TSclust] is a wrapper to several dissimilarity measures for clustering time series. 
Some of us maintain the pdc clustering package [@pdc-paper], which is contained in TSclust and we saw that researchers use the pdc approach but only cite the TSclust package.
-->

@@

In our opinion, total citation metrics, number of users, downloads per month, github stars and similar may provide a coarse measure for the impact of a software package, even though it is important to note the shortcomings we described above.
